Meta-analysis

### 2021-01-29 03_Prep_data.Rmd
Edits mainly spelling and grammar

```{r filterDMI_trials}
DMI_Trials <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref) %>%
   pull()

PM_MB_dat <- 
   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials,]
```

Now remove any non-DMI treatments or controls
```{r}
PM_MB_dat <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control" |
             fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")
```

@@

We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).

@@

   V_yield <-
      (PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates[1] * 
          (LSD / Tcrit) ^ 2) / 2 
   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

@@

PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"] <- 
   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"]^2

PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,]$Y_error_type <-
   "SamplingVariance"

@@

Lets look at the association between mean squares and yield to see if there is a more typical association between yield and variance.

@@

These categorical variables are named:
   - **Early**: First fungicide application was prior to first sign of disease. 
   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign. 
   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

@@

```{r define_trial}
PM_MB_dat <-
   PM_MB_dat %>%
   mutate(trial = paste(
      trial_ref, 
      year, 
      location, 
      host_genotype,
      row_spacing, 
      sep = "_")) %>%
   select(trial_ref, trial, everything())
```

@@

Earlier, in section [Fungicide Doses](#fungicide-doses) we noted there were different doses of propiconazole, which might influence our analysis. 
The current label for custodia [PER82104](http://permits.apvma.gov.au/PER82104.PDF), Containing: 120 g/L azoxystrobin and 200 g/L tebuconazole, recommends between 300 ml - 600 ml of the tebuconazole fraction per hectare, equivalent to 60 - 120 grams per hectare. 
These label rates are assumed to be the same for propiconazole infering these concentrations might be within the recommended rates. 
It is also worth noting the APVMA permit [PER13979](http://permits.apvma.gov.au/PER13979.PDF) which allows the use of Tebuconazole between 62.35 g / ha and 83 g / ha depending on the product formulation.

@@

********
## Remove unnecersary variables

```{r saveDat}
PM_MB_dat <-
   PM_MB_dat %>%
   select(-c(trial_dose,
             fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
             dose, fungicide_application_4, fungicide_application_5,
             fungicide_application_6, fungicide_application_7)) 
```

## Final data check  
Now we have defined our treatments lets inspect plots to visualise how well the data compares across the trial years and locations?

@@

PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "control",
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             ),
          id = row_number(),
          vi = yield_error,
          n = replicates) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype,
      spray_management,
      fungicide_ai,
      grain_yield.t.ha.,
      yield_gain,
      vi,
      vi2,
      n,
      id)
```

>>>>

```{r filterDMI_trials}
DMI_Trials <-
   PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   distinct(trial_ref) %>%
   pull()

PM_MB_dat <-
   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials, ]
```

Now remove any non-DMI treatments or controls
```{r}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   )
```

@@

We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Ngugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).

@@

   V_yield <-
      (PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates[1] * 
          (LSD / Tcrit) ^ 2) / 2 
   # method - Ngugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

@@

PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] <-
   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] ^ 2

PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, ]$Y_error_type <-
   "SamplingVariance"
```

@@

Let's look at the association between mean squares and yield to see if there is a more typical association between yield and variance.

@@

These categorical variables are named:

   - **Early**: First fungicide application was prior to first sign of disease. 
   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign. 
   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

@@

```{r define_trial}
PM_MB_dat <-
   PM_MB_dat %>%
   mutate(trial = paste(trial_ref,
                        year,
                        location,
                        host_genotype,
                        row_spacing,
                        sep = "_")) %>%
   select(trial_ref, trial, everything())
```

@@

Earlier, in section [Fungicide Doses](#fungicide-doses) we noted there were different doses of propiconazole, which might influence our analysis. 
The current label for Custodia [PER82104](http://permits.apvma.gov.au/PER82104.PDF), containing: 120 g/L azoxystrobin and 200 g/L tebuconazole, recommends between 300 ml - 600 ml of the tebuconazole fraction per hectare, equivalent to 60 - 120 grams per hectare. 
These label rates are assumed to be the same for propiconazole inferring these concentrations might be within the recommended rates. 
It is also worth noting the APVMA permit [PER13979](http://permits.apvma.gov.au/PER13979.PDF) which allows the use of tebuconazole between 62.35 g / ha and 83 g / ha depending on the product formulation.

@@

********

## Remove unnecessary variables

```{r saveDat}
PM_MB_dat <-
   PM_MB_dat %>%
   select(
      -c(
         trial_dose,
         fungicide_timing_1,
         fungicide_timing_2,
         fungicide_timing_3,
         dose,
         fungicide_application_4,
         fungicide_application_5,
         fungicide_application_6,
         fungicide_application_7
      )
   ) 
```

## Final data check  
Now we have defined our treatments. Let's inspect plots to visualise how well the data compares across the trial years and locations.

@@

PM_MB_dat <-
   PM_MB_dat %>%
   mutate(
      spray_management =
         factor(
            spray_management,
            c(
               "control",
               "Early",
               "Recommended",
               "Recommended_plus",
               "Late",
               "Late_plus"
            )
         ),
      id = row_number(),
      vi = yield_error,
      n = replicates
   ) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype,
      spray_management,
      fungicide_ai,
      grain_yield.t.ha.,
      yield_gain,
      vi,
      vi2,
      n,
      id
   )
```

### 2021-01-29 04_MetaAnalysis.Rmd
Edits mainly spelling and grammar

A secondary question to this aim is: given the time at which the first spray occurred is a second spray provide worthwhile yield protection.

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_MB_dat
)

@@

Lets try the model with an implied simpler variance-covariance matrix "compound symetry" ("CS") to examine if unstructured matrix is suitable.
```{r}
PM_mv_cs <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "CS",
   control = list(optimizer = "optim"),
   data = PM_MB_dat
)

@@

Lets present the meta-analysis results for the moderator variables in a forest style plot.
First lets create a table of the results.

@@

# adjust estimates to show absolute means
results_mv <-
   results_mv[2:6, ] %>%
   mutate(Effect = Effect + results_mv$Effect[1]) %>%
   mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
   mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
   bind_rows(results_mv[1, ]) %>%
   mutate(index = c(2:6, 1)) %>%
   arrange(index)

@@

kable(results_mv[, 2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table ##: Estimated mean mungbean yields for each spray schedule treatment used for mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia. Yield estimates were calculated from the network meta-analysis of data obtained from grey literature reports. Z and P values indicate statistical significance in comparison to the intercept.")

@@

Lets investigate the treatment contrasts

@@

### Forest plot of trial treatment effect per trial
Lets look at the trial variability in this model with a forest plot
```{r forestP, eval=FALSE, fig.height=40, fig.width=17, include=FALSE}
# THIS NEEDS TO BE FIXED
source(here("R/change_labels.R"))
source(here("R/forest_rows.R"))

### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
index1 <- PM_MB_dat %>%
   mutate(ID = seq_along(trial_ref)) %>%
   mutate(spray_management =
             factor(
                spray_management,
                levels = c(
                   "Early",
                   "Late",
                   "Recommended",
                   "Recommended_plus",
                   "Late_plus"
                )
             )) %>%
   arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
   mutate(ID2 = order(ID)) %>%
   pull(ID2)

### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
### this list can be used below to reference where to plot each variable
rows1 <- forest_rows(
   head_row = 186,
   ord_var = PM_MB_dat$spray_management,
   index = index1,
   gap = 5,
   row_offset = -2
)

### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
polys <- data.frame(
   ref = change_labels(names(coef(PM_mv))),
   x = c(coef(PM_mv)[1], coef(PM_mv)[1] + coef(PM_mv)[2:6]),
   ci.lb = c(PM_mv$ci.lb[1], PM_mv$ci.lb[1] + PM_mv$ci.lb[2:6]),
   ci.ub = c(PM_mv$ci.ub[1], PM_mv$ci.ub[1] + PM_mv$ci.ub[2:6])
)[c(2, 5, 3, 4, 6, 1), ]
polys$rows <- rows1$pred_row - 1.5

>>>>

A secondary question to this aim is: given the time at which the first spray occurred does a second spray provide worthwhile yield protection.

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_MB_dat
)

@@

Let's try the model with an implied simpler variance-covariance matrix "compound symmetry" ("CS") to examine if unstructured matrix is suitable.
```{r}
PM_mv_cs <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "CS",
   control = list(optimizer = "optim"),
   data = PM_MB_dat
)

@@

Let's present the meta-analysis results for the moderator variables in a forest style plot.
First Let's create a table of the results.

@@

# adjust estimates to show absolute means
results_mv <-
   results_mv[2:6,] %>%
   mutate(Effect = Effect + results_mv$Effect[1]) %>%
   mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
   mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
   bind_rows(results_mv[1,]) %>%
   mutate(index = c(2:6, 1)) %>%
   arrange(index)

@@

kable(results_mv[, 2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table ##: Estimated mean mungbean yields for each spray schedule treatment used for mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia. Yield estimates were calculated from the network meta-analysis of data obtained from grey literature reports. Z and P values indicate statistical significance in comparison to the intercept.")
```

@@

Let's investigate the treatment contrasts

@@

### Forest plot of trial treatment effect per trial
Let's look at the trial variability in this model with a forest plot
```{r forestP, eval=FALSE, fig.height=40, fig.width=17, include=FALSE}
# THIS NEEDS TO BE FIXED
source(here("R/change_labels.R"))
source(here("R/forest_rows.R"))

# Sort and arrange data-frame accordingly and produce a index vector to inform
# the order of each "Trial" on the plot
index1 <- PM_MB_dat %>%
   mutate(ID = seq_along(trial_ref)) %>%
   mutate(spray_management =
             factor(
                spray_management,
                levels = c(
                   "Early",
                   "Late",
                   "Recommended",
                   "Recommended_plus",
                   "Late_plus"
                )
             )) %>%
   arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
   mutate(ID2 = order(ID)) %>%
   pull(ID2)

# Use forest rows function to return a list of where to place on the plot:
# sub-titles, each trial row, and summary prediction for each treatment.
# this list can be used below to reference where to plot each variable
rows1 <- forest_rows(
   head_row = 186,
   ord_var = PM_MB_dat$spray_management,
   index = index1,
   gap = 5,
   row_offset = -2
)

# A data-frame of meta-model coefficients used to produce the summary polygons
# for each treatment
polys <- data.frame(
   ref = change_labels(names(coef(PM_mv))),
   x = c(coef(PM_mv)[1], coef(PM_mv)[1] + coef(PM_mv)[2:6]),
   ci.lb = c(PM_mv$ci.lb[1], PM_mv$ci.lb[1] + PM_mv$ci.lb[2:6]),
   ci.ub = c(PM_mv$ci.ub[1], PM_mv$ci.ub[1] + PM_mv$ci.ub[2:6])
)[c(2, 5, 3, 4, 6, 1), ]
polys$rows <- rows1$pred_row - 1.5
